\section{Projects}
\vspace*{-6pt}

\project{Fitness Club CRM}{December 2020 {-} June 2021}{The Barking Dog Entertainment 愛吠的狗}

\small
Maintenance works on a CRM system of a major Taiwanese chain of fitness clubs and gyms.
Implemented several new types of customer contracts, including backend integrations, payment, React UI,
and PDF generation. Implemented automatic membership prolongation during government lockdowns.
Rebuilt cloud infrastructure and CI/CD pipelines.

\projectweb{Moshi Official Website}{https://moshi.com/en/}{Summer 2020}{Contracted for Cogini HK Limited}

\small
Web-facing e-commerce website generated using Gatsby and GraphQL. Elixir and React-based CMS for managing product variants, prices, descriptions, and images.
Checkout integrated with Shopify.

\projectweb{Print Your Own Foto}{https://gitlab.com/moroz2137/gen\_collage}{September {–} October 2020}{Freelance}

\small
Web-based editor for crafting personalized photo collages, with support for Instagram-like filters, image frames, text overlay, cropping.
Never finished or deployed due to the client running out of funds.

\projectweb{Horizon-Sim}{https://www.horizon-sim.com}{2019}{Access AP, TW}

\small
Custom e-commerce solution built with Elixir, Phoenix, and React.js, with custom payment gateway integration.
The client went out of business during COVID.

\project{Beacon Parameter Management System}{October {–} November 2018}{Access AP, TW}

\small
Full stack Single-Page Application built for a Japanese client, used to manage serial numbers of mass-produced
devices, generate CSV reports and QR code sheets.

\projectweb{Injobs.pl}{https://www.injobs.pl}{April {–} August 2017}{Injobs.pl Sp. z o. o., PL}

\small
Job board with company and applicant profiles, promoted job ads, and custom payment gateway integration, built with Ruby on Rails. Rewritten by the client.

